Generate data for NOBA cod ensemble modeling

### 2020-05-22 NOBAcod.Rmd
partial functions for ANNAGECATCH reading

annwtage <- weightage %>%
  group_by(species, agecl, time) %>%
  summarise(wtage = mean(atoutput)) %>%
  filter(time %in% survtime)

wageplot <- ggplot(annwtage, aes(time, wtage)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")

@@

Looks like the annagecatch output is only numbers and not weights.

@@

>>>>

annwtage <- weightage %>%
  group_by(species, agecl, time) %>%
  summarise(wtage = mean(atoutput)) %>%
  filter(time %in% (survtime))

boxwtage <- weightage %>%
  mutate(wtage = atoutput) %>%
  filter(species %in% c("North_atl_cod"),
         polygon %in% c(1,7,24,30,38,45),
         agecl %in% c(16:20))

wtagedat <- boxwtage

wageplot <- ggplot(wtagedat, aes(time, wtage)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " "))

wageplot + facet_wrap(c("polygon"), scales="free_y")

@@

UPDATE: there is a difference between the annage weight at age and that calculated using 'calc_age2length'. While the results from the standard nc output look reasonable for NOBA cod, the annage weight at age is half that for the standard (and half what real cod would be). More worrisome, the oldest age classes have smaller average weight at age than some younger ones. I cannot think of why this would be. Until we are sure the annage weight output is correct, we will instead interpolate the weight at age output of 'calc_age2length" for use as assessment input.

Looks like the annagecatch output is only numbers and not weights. We don't get weight at age from fisheries usually so this is fine.

@@

New function `load_fisheries` needed to load the fishery specification file (a .csv), similar to `load_fgs`:

```{r load_fisheries}

load_fisheries <- function(dir = getwd(), file_fish){
  if (is.null(dir)) {
    file.fish <- file_fish
  } else {
    file.fish <- file.path(dir, file_fish)
  }
  result <- read.table(file = file.fish, sep = ",",
    header = TRUE, stringsAsFactors = FALSE)
  return(result)
}
```

Call `load_fisheries` within `load_nc_annage` to rename select_variable as used in ANNAGECATCH.nc:

```{r addsnippet}

select_variable <- c("Catch", "Discard")
dir <- here("atlantisoutput","NOBA_march_2020")
file_fish <- "NoBAFisheries.csv"

#starting at line 115 in current load_nc_annage

if(select_variable %in% c("Catch", "Discard")){
    #read in fleet names
    fleetnames <- load_fisheries(dir = dir, file_fish = file_fish)
    for(i in select_variable){
      sv <-paste0(i, "_", fleetnames$Code)
      sv1 <- c()
    }
  }
